### 2017-06-04 sheets/talk-6/sheet-6.tex
Solutions for 6: Greatest lower bound and least upper bound

@@

>>>>

\begin{answer}
  Let $(A, \le)$ be a poset concidered as a category and $I$ a set.
  A \demph{lower bound} of a family $(x_i)_{i\in I}$ is an element $a \in A$, s.\,t. $\forall i \in I: a \le x_i$.
  $z \in A$ is a \demph{greatest lower bound} of this family if $\forall a \in A: \text{$a$ is a lower bound} \Rightarrow a \le z$.

  Let $z$ be a greatest lower bound of the family $(x_i)_{i\in I}$. We show that $z$ is a product of $(x_i)_{i\in I}$.
  \begin{proof}
    We first have to define a family of maps $\Bigl(z \toby{p_i} x_i\Bigr)_{i \in I}$.
    This is trivial since we have $\forall i \in I: z \le x_i$.
    Now let $a \in A$ be and objects and let $\Bigl(a \toby{f_i} x_i\Bigr)_{i \in I}$ be a family of maps from $a$.
    The existing of this maps means that $a$ is a upper bound of $(x_i)_{i\in I}$.
    Now by definition of least upper bound, $a \le z$, thus we have a arrow $\bar{f} \from a \to z$.
    All arrows are unique, thus $\bar{f}$ is unique and the diagram commutes. \qedhere
  \end{proof}
\end{answer}

@@

\begin{answer}
  Let $(A, \le)$ be a poset concidered as a category and $I$ a set.
  A \demph{upper bound} of a family $(x_i)_{i\in I}$ is an element $a \in A$, s.\,t. $\forall i \in I: x_i \le z$.
  $z \in A$ is a \demph{least upper bound} of this family if $\forall a \in A: \text{$a$ is a upper bound} \Rightarrow z \le a$.

  Let $z$ be a least upper bound of the family $(x_i)_{i\in I}$. We show that $z$ is a coproduct of $(x_i)_{i\in I}$.
  \begin{proof}
    We first have to define a family of maps $\Bigl(x_i \toby{p_i} z\Bigr)_{i \in I}$.
    This is trivial since we have $\forall i \in I: x_i \le a$.
    Now let $a \in A$ be and objects and let $\Bigl(x_i \toby{f_i} a\Bigr)_{i \in I}$ be a family of maps to $a$.
    The existing of this maps means that $a$ is a lower bound of $(x_i)_{i\in I}$.
    Now by definition of least lower bound, $z \le a$, thus we have a arrow $\bar{f} \from z \to a$.
    All arrows are unique, thus $\bar{f}$ is unique and the diagram commutes. \qedhere
  \end{proof}
\end{answer}
